Supplementary Information

### 2020-07-29 doc/manuscript/MEE_manuscript_SI.Rmd
Update MEE_manuscript_SI.Rmd
recording methods described in [this issue](https://github.com/EcoClimLab/ForestGEO_dendro/issues/24)

DBH can be reconstructed outside-in (based on recent $DBH$, subtracting growth recorded in tree rings) or inside-out (summing $\Delta r$ from the inside out). 
We generally gave precedence to the outside-in approach.
Specifically, when $DBH$ was taken at the time of coring,  
At some of our sites where DBH was not taken at the time of coring (*SCBI*,), DBH measurements taken before or slightly after the time of coring could be used.
(see [issue #19 in ForestGEO_dendro](https://github.com/EcoClimLab/ForestGEO_dendro/issues/19))
If before, ... 
If after...
For all outside-in reconstructions, if a negative $DBH$ was predicted...

>>>>

For each core, $DBH$ can be reconstructed outside-in (based on recent $DBH$, subtracting growth recorded in tree rings) or inside-out (summing $\Delta r$ from the inside out). 
We generally gave precedence to the outside-in approach.
Specifically, when $DBH$ was taken at the time of coring,  
At some of our sites where DBH was not taken at the time of coring (*SCBI*,), DBH measurements taken before or slightly after the time of coring could be used.
(see [issue #19 in ForestGEO_dendro](https://github.com/EcoClimLab/ForestGEO_dendro/issues/19))
If before, ... 
If after...
For all outside-in reconstructions, if a negative $DBH$ was predicted...

When there were more than one cores for a tree, the $DBH$ reconstructions from each core were averaged to produce a single estimate of the tree's $DBH$ through time. 
When the start or end dates of the records from the cores differed, we extrapolated growth of the shorter core to match the years covered by the longer core. 
Specifically, to fill in years at the more recent end, we assumed that the average growth rate of the ten years prior to the missing records applied to the missing years. 
To fill in years at the beginning of the tree's lifespan, we likewise assumed that the ten years adjacent to the missing record applied to the missing years; however, if this yielded a negative $DBH$ estimate for the earliest year in the reconstruction, we divided the existing minimum $DBH$ by number of years missing and applied that value to each year.
We note that these reconstructed growth records were used only for the reconstruction of $DBH$ and were not included as response variables in any of our analyses.
